%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Relevant Coursework}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {Honors General Chemistry} % Course
    {Three quarter honors sequence covering quantum mechanics, orbital theory, and bonding.} % Description
%---------------------------------------------------------
\cvskill
    {Organic Chemistry} % Course
    {Three quarter sequence covering organic reactions, bonding theory, and methods of analysis.} % Description
%---------------------------------------------------------
\cvskill
    {General Chemistry Laboratory} % Course
    {Training in analytical, inorganic, physical, and synthetic techniques.} % Description
%---------------------------------------------------------
\cvskill
    {Organic Chemistry Laboratory} % Course
    {Intro to techniques,such as separation, purification, and spectroscopy.} % Description
%---------------------------------------------------------
\cvskill
    {Engineering Computation (MATLAB)} % Course
    {Intro to solution of engineering problems using computational methods.} % Description
%---------------------------------------------------------
\cvskill
    {Material \& Energy Balances} % Course
    {Stead \& time-based material \& energy balances using DOF analysis, kinetics, and equilibrium.} % Description
%---------------------------------------------------------
\cvskill
    {Chemical Engineering Thermodynamics} % Course
    {Thermodynamic behavior of substances, solution properties, and phase equilibrium.} % Description
%---------------------------------------------------------
\cvskill
    {Data Structures for Data Science} % Course
    {Simple Python data structures, recursion, \& object-oriented programming.} % Description
%---------------------------------------------------------
\cvskill
    {Data Structures \& Algorithms for Data Science} % Course
    {Programming techniques, such as encapsulations, interfaces, and advanced data structures.} % Description
%---------------------------------------------------------
\cvskill
    {Physics: Mechanics} % Course
    {Calculus-based physics covering vectors, motion, work, energy, and rotational kinematics.} % Description
%---------------------------------------------------------
\cvskill
    {Physics: Electricity \& Magnetism} % Course
    {Calculus-based physics covering charges, electric fields, capacitors, currents, and resistance.} % Description
%---------------------------------------------------------
\cvskill
    {Physics: Fluids, Waves, \& Thermodynamics} % Course
    {Calculus-based physics covering fluid mechanics, sound, entropy, optics, and diffraction.} % Description
%---------------------------------------------------------
\cvskill
    {Physics Laboratory: Electricity \& Magnetism} % Course
    {Lab course covering circuits, oscillations, resonance, damping, and magnetic fields.} % Description
%---------------------------------------------------------
\cvskill
    {Calculus \& Analytic Geometry} % Course
    {Vector geometry, partial differentiation, double-triple integration, and extrema.} % Description
%---------------------------------------------------------
\cvskill
    {Differential Equations} % Course
    {Ordinary \& partial differential equations, Laplace transforms, and series solutions.} % Description
%---------------------------------------------------------
\cvskill
    {Vector Calculus} % Course
    {Change of variables in multiple integrals, line integrals, Taylor series, and surface integrals.} % Description
%---------------------------------------------------------
\cvskill
    {Linear Algebra} % Course
    {Matrix algebra, elimination, eigenvalues \& eigenvectors, and MATLAB computational solutions.} % Description
%---------------------------------------------------------
\cvskill
    {Chemical Reaction Engineering} % Course
    {Principles of chemical reactor analysis and design, selectivity optimization in multiple reactions.} % Description
%---------------------------------------------------------
\cvskill
    {Inorganic Chemistry} % Course
    {Structural theory involving s, p, \& unfilled d orbitals. } % Description
%---------------------------------------------------------
\cvskill
    {Biochemical Structure \& Function} % Course
    {Introduction to biochemistry from a structural/ functional viewpoint.} % Description
%---------------------------------------------------------
\cvskill
    {Biochemical Energetics \& Metabolism} % Course
    {An introduction to the metabolic reactions in the cell which produce and utilize energy.} % Description
%---------------------------------------------------------
\cvskill
    {Molecular Biology} % Course
    {Molecular mechanisms, applications of the central dogma, genome structure \& function.} % Description
%---------------------------------------------------------
\cvskill
    {Fluid Mechanics} % Course
    {Kinematics and equation of motion; hydrostatics; Bernoulli’s equation; viscous flows.} % Description
%---------------------------------------------------------
\cvskill
    {Heat Transfer} % Course
    {Conduction, convection, radiation heat transfer; design of heat exchangers. } % Description
%---------------------------------------------------------
\cvskill
    {Mass Transfer} % Course
    {Diffusive and convective mass transfer in solids, liquids, and gasses; steady \& unsteady state.} % Description
%---------------------------------------------------------
\cvskill
    {Experimental Techniques} % Course
    {Principles and practice of measurement and control and the design and conduct of experiments.} % Description
%---------------------------------------------------------
\cvskill
    {Probability and Statistical Methods for Engineers} % Course
    {Probability theory, conditional probability, Bayes theorem, discrete random variables.} % Description
%---------------------------------------------------------
\cvskill
    {Recombinant DNA Laboratory} % Course
    {Introduction to molecular biology and recombinant DNA techniques.} % Description
%---------------------------------------------------------
\cvskill
    {Biology of Cancer} % Course
    {Cellular/genetic changes that characterize the development/progression of cancer.} % Description
%---------------------------------------------------------
\cvskill
    {Pharmacology and Toxicology} % Course
    {A survey of the biochemical action of drugs/toxins, as well as their absorption/excretion.} % Description
%---------------------------------------------------------
\cvskill
    {Microbiology Laboratory} % Course
    {Discussion of the structure, growth, physiology, and molecular genetics of prokaryotes.} % Description
%---------------------------------------------------------
\cvskill
    {Foundations in NanoEngineering: Biochemical Principles} % Course
    {Principles of biochemistry tailored to nanotechnologies.} % Description
%---------------------------------------------------------
\cvskill
    {Materials Science and Engineering} % Course
    {Structure and control of materials: metals, ceramics, glasses, and semiconductors.} % Description
%---------------------------------------------------------
\cvskill
    {Thermodynamics of Materials} % Course
    {Fundamental laws of thermodynamics for simple substances.} % Description
%---------------------------------------------------------
\cvskill
    {Chemical Process Dynamics and Control} % Course
    {Examination of dynamic linear and linearized models of chemical processes.} % Description
%---------------------------------------------------------
\cvskill
    {Separation Processes} % Course
    {Principles of analysis and design of systems for separation of components.} % Description
%---------------------------------------------------------
\cvskill
    {Chemical Plant and Process Design} % Course
    {Principles of chemical process design and economics. Process flow diagrams.} % Description
%---------------------------------------------------------
\cvskill
    {Chemical Engineering Process Laboratory} % Course
    {Laboratory projects in the areas of applied chemical research and unit operations.} % Description
%---------------------------------------------------------
\end{cvskills}
