%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Research Assistant} % Job title
{UC San Diego: School of Medicine - Center for ALS Research \& Therapy} % Organization
{La Jolla, CA} % Location
{September 2020 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked with Dr. John Ravits to identify mechanisms \& therapeutic targets of neuronal degeneration in ALS, due to repeat expansions in C9orf72.}
    \item {Identify proteins binding to G\textsubscript{4}C\textsubscript{2} \& G\textsubscript{2}C\textsubscript{4} repeat expansions in C9orf72 RNA transcripts of cells afflicted by ALS \& determine full sequence and structure of repeat expansions.}
    \item {Implement various techniques to investigate appropriate targets for antisense oligonucleotide therapies.}
    \item {Performed lab chores and contributed to the design, execution, and interpretation of experiments.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Research Assistant} % Job title
{UC San Diego: School of Medicine - Center for Neural Repair} % Organization
{La Jolla, CA} % Location
{February 2020 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked with Dr. Armin Blesch on identifying mechanisms influencing neuronal plasticity and regeneration in the mammalian nervous system.}
    \item {Implemented various techniques to investigate the potential role of neural stem cells and biomaterials in spinal cord regeneration.}
    \item {Assisted with projects addressing the structural changes associated with pain development after spinal cord injury.}
    \item {Validated findings in rodent models through gene therapy.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Computational Neuroscience Intern} % Job title
%{University of California, San Diego - School of Medicine - Department of Neuroscience} % Organization
{UC San Diego: National Center for Microscopy and Imaging Research} % Organization
{La Jolla, CA} % Location
{August 2019 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Computational neuroscience study in software development for large-scale biomedical image analysis.}
    \item {Implemented deep neural networks and image processing pipelines with regard to learning, memory, and inter-neuron communication.}
    \item {Developed a Python program to generate colored meshes from label volumes and isolate unique regions.}
  \end{cvitems}
}
%---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {UC San Diego: School of Medicine - Altman Clinical \& Translational Research Institute} % Organization
    {La Jolla, CA} % Location
    {September 2019 - April 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Dr. Derek Welsbie on developing a neuroprotective strategy for glaucoma.}
        \item {Implemented various techniques to identify drug targets in primary mouse and stem cell-derived human retinal ganglion cells.}
        \item {Assisted with projects addressing the signaling pathway in retinal ganglion cell death.}
        \item {Validated findings in rodent models using gene therapy.}
        \item {Performed lab chores and helped with the design, performance, and interpretation of experiments.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Digital Pathology Intern} % Job title
    {University of California, San Diego - School of Medicine - Department of Pathology} % Organization
    {La Jolla, CA} % Location
    {September 2018 - August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Digital pathology research group verifying the viability of digital scans of tissue slides to replace physical samples.}
        \item {Helped pull slides from archives, scanned slides with a digital slide scanner, and shadowed Dr. Valasek’s diagnoses of the slides.}
        \item {Developed and maintained a database comparing the diagnoses between a physical slide and a digital copy.}
      \end{cvitems}
    }
%---------------------------------------------------------
 \cventry
    {Mechatronics Laboratory Intern} % Job title
    {University of California, Irvine - Claire Trevor School of the Arts} % Organization
    {Irvine, CA} % Location
    {July 2017 - September 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with Professor Simon Penny on the Orthogonal project that attempted to build a self-sailing sailboat, controlled by a radio interface.}
        \item {Tasked with physically building the boat and working with Arduino micro-controllers to control a DC motor for autonomy.}
        \item {Applied rudder control through various integrated circuits and configured radio communication between wireless nRF modules.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
