%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
    {Technical Writer} % Job title
    {Illumina} % Organization
    {San Diego, CA} % Location
    {July 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to process improvement and optimization in manufacturing.}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
    {Scientist, Drug Discovery Manufacturing} % Job title
    {Thermo Fisher Scientific} % Organization
    {Carlsbad, CA} % Location
    {July 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Manufactured and qualified lab products following standard operating procedures.}
        \item {Performed buffer preparation, column purification, chromatography, SDS-PAGE, Western blots.}
        \item {Executed TR-FRET, immunofluorescence, radioactive, \& protein concentration assays.}
        \item {Assisted with process improvement projects to reduce waste and raise productivity.}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
{Research Assistant} % Job title
{UC San Diego: School of Medicine - Center for Neural Repair} % Organization
{La Jolla, CA} % Location
{February 2020 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked with Dr. Armin Blesch on identifying mechanisms influencing neuronal plasticity and regeneration in the mammalian nervous system.}
    \item {Implemented various techniques to investigate the potential role of neural stem cells and biomaterials in spinal cord regeneration.}
    \item {Assisted with projects addressing the structural changes associated with pain development after spinal cord injury.}
    \item {Performed mouse perfusions and analyzed two-photon excitation microscopy data.}
    \item {Validated findings in rodent models through gene therapy.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Research Assistant} % Job title
{UC San Diego: School of Medicine - Center for ALS Research \& Therapy} % Organization
{La Jolla, CA} % Location
{September 2020 - November 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked with Dr. John Ravits to identify mechanisms \& therapeutic targets of neuronal degeneration in ALS.}
    \item {Researched association of nucleolar stress and translation dysfunction on ribosomal biogenesis in sALS, C9-ALS and SOD1-dependent ALS.}
    \item {Developed protocol to identify proteins binding to G\textsubscript{4}C\textsubscript{2} \& G\textsubscript{2}C\textsubscript{4} repeat expansions in C9orf72 RNA transcripts of cells afflicted by ALS \& determine full sequence and structure of repeat expansions.}
    \item {Implemented various techniques to investigate appropriate targets for antisense oligonucleotide therapies.}
    \item {Assisted with cryostorage organization, confocal microscopy, immunostaining, and cell culture.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Computational Neuroscience Intern} % Job title
%{University of California, San Diego - School of Medicine - Department of Neuroscience} % Organization
{UC San Diego: National Center for Microscopy and Imaging Research} % Organization
{La Jolla, CA} % Location
{August 2019 - April 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Computational neuroscience study in software development for large-scale biomedical image analysis.}
    \item {Implemented deep neural networks and image processing pipelines with regard to learning, memory, and inter-neuron communication.}
    \item {Developed a Python program to generate colored meshes from label volumes and isolate unique regions.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{Undergraduate Research Assistant} % Job title
{UC San Diego: Altman Clinical \& Translational Research Institute} % Organization
{La Jolla, CA} % Location
{September 2019 - April 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Worked with Dr. Derek Welsbie on developing a neuroprotective strategy for glaucoma.}
    \item {Implemented various techniques to identify drug targets in primary mouse and stem cell-derived human retinal ganglion cells.}
    \item {Assisted with projects addressing the signaling pathway in retinal ganglion cell death.}
    \item {Validated findings in rodent models using gene therapy.}
  \end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
